---
title       : Predicting Custom Vehicle's Mileage (MPG)
author      : Rubina Sattar
job         : Coursera Student
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
hitheme     : tomorrow      # 
widgets     : [mathjax]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
output: html_document
---

## Introduction

This shiny application allows an user to design their dream car and then predict the mileage in Miles per Gallon (MPG) 
for their dream car.

---
## Application Inputs (via GUI)

The user can select any or all of the following inputs to customize their car:

. Cylinder

. Displacement

. Horsepower

. Weight

. Automatic or Manual

---
## Application Logic

Applying the method = glm (Generalized Linear Regression Model), we crete a fit  
model from which we will determine the prediction model.

```{r}
fit <- train(mpg ~ cyl+disp+hp+wt+am, method = "glm", data = mtcars)

result <- function(cyl,disp,hp,wt,am) {
  s <- cbind(cyl,disp,hp,wt,am)
  res <- predict(fit,s)
  as.character(res)
}
```

---
## Application Prediction

Predicting the output (target, MPG) from the best fit model with:
```{r}
output$prediction <- renderPrint({result(input$variable1,input$variable2,input$variable3,
        input$variable4,input$variable5)})
```
--- 
## Application Output
This is a screenshot of the deployed shiny application. It was tested and worked for various combinations of numeric inputs. Feel free to give it a try!

--- 



